Improving Code Completion in Pharo\\Using N-gram Language Models

### 2020-02-19 ACM/abstract.tex
Removed lipsum package and acmart.bib
Improved the title

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
\usepackage{lipsum}

\title{Usage of N-gram models to improve autocompletion in Pharo}
\author{Myroslava Romaniuk}
\affiliation{\institution{Ukrainian Catholic University}}
\email{romaniuk@ucu.edu.ua}

@@

Therefore, in Pharo our idea is to have a sorting strategy based on an n-gram model, on top of the actual completion engine that works by analysing AST information of the source code, having \oz{\sout{actually}} utilised structural information\oz{What is structural information and how do you utilise it?}. In this case, we are able to get semantically-appropriate results based on type whenever possible, and then sort\oz{\sout{ing}} the results by relevance \oz{\sout{will help} which allows us to} suggest much more accurate tokens for when the type is not known\oz{\oz{ (as Pharo is a dynamically typed language)} You can mention that at the beginning of the sentence}.

>>>>

\title{Improving Code Completion in Pharo\\Using N-gram Language Models}
%\title{Usage of N-gram models to improve autocompletion in Pharo}
\author{Myroslava Romaniuk}
\affiliation{\institution{Ukrainian Catholic University}}
\email{romaniuk@ucu.edu.ua}

@@

Therefore, in Pharo our idea is to have a sorting strategy based on an n-gram model, on top of the actual completion engine that works by analysing AST information of the source code, having \oz{\sout{actually}} utilised structural information\oz{What is structural information and how do you utilise it?}. In this case, we are able to get semantically-appropriate results based on type whenever possible, and then sort\oz{\sout{ing}} the results by relevance \oz{\sout{will help} which allows us to} suggest much more accurate tokens for when the type is not known\oz{\sout{ (as Pharo is a dynamically typed language)} You can mention that at the beginning of the sentence}.
